\documentclass[11pt]{article}

% Use wide margins, but not quite so wide as fullpage.sty
\marginparwidth 0.5in 
\oddsidemargin 0.25in 
\evensidemargin 0.25in 
\marginparsep 0.25in
\topmargin 0.25in 
\textwidth 6in \textheight 8 in
% That's about enough definitions

\usepackage{multirow}
\usepackage{tabularx}

\begin{document}
%\hfill\vbox{\hbox{Gius, Mark}
%		\hbox{Cpe 456, Section 01}	
%		\hbox{Lab 1}	
%		\hbox{\today}}\par
%
%\bigskip
%\centerline{\Large\bf Lab 1: Security Audit}\par
%\bigskip
\author{Mark Gius}
\title{Lab 1: Security Audit}
\maketitle

\section{System Description}

The system is a low-powered Atom PC, small form factor 
(it is less than 12" on each side, and about 3" tall), 
with a 320GB hard drive and 2GB of ram.  
The system is located in my bedroom in a house in San Luis Obispo, 
on top of another computer.  It is plugged into a surge protector, 
but not a UPS.  The surge protector is shared with several other computers.
The system has no input devices plugged into it 
(keyboard, mouse, webcam, etc).

The system is connected to the internet via a switch in my bedroom 
that is shared with several other desktops. The bedroom switch connects 
to a shared house switch via a cable that runs along the floor of 
the hallway leading to my bedroom.  The shared workgroup switch 
has connects to a Linksys router running DD-WRT (linux), connected to 
a DSL modem (local ATT affiliate ISP).

\section{Threat Analysis}

\begin{tabularx}{\textwidth}{| X || X | X X |}
	\hline
	\textbf{Threat} & & & \\
	\hline
	\multirow{4}{*}{Power Loss}
		& \multirow{2}{*}{Goals violated}
			& Availability 
				& The system is completely unavailable in the event 
				  of a power loss \\
			\cline{3-4}
			& % multirow empty space
			& Integrity 
				& Power loss is well known to cause data corruption \\
		\cline{2-4}
      & Vulnerability 
			& \multicolumn{2}{ p{7.0cm} |}{
				Random power outage (or malicious conduct) could cause power loss
			   to the system} \\
		\cline{2-4}
		& Controls & \\
	\hline

\end{tabularx}

\end{document}
